Luminance constancy under fixed geometry

### 2018-01-16 Draft2/draft2.tex
small edits
more edits

% WHAT STORY DO WE WANT TO TELL ABOUT THE RESULTS
%  1) Case 0 -- work out effect of sources of internal noise - isomerization and AMA -- without any external "noise", where external "noise" is the effect of variability in object extrinsic scene factors (illumination, surrounding objects). 
%                      Also establish the rendering noise is einsy relative to whatever else we're doing.
%  2) Move to Case 1 -- what happens when we introduce color variability into the target.  This may not be of interest to the psychophysics, but none-the-less seems interesting to know as one ponders lightness constancy.
%  3) On to Case 2 -- here the question is, do we keep varying target color, or do we fix target color and vary illumination?  In any case, this isn't too hard a case if the other objects remain fixed, because then contrast coding basically normalizes out a lot of the variation, and it's only the spectral variation that might screw things up.  But, that's why we run case 3.
%  4) Do we run a case where the relative spectrum of the illuminant stays fixed and we only vary intensity?
%  4) On to Case 3 --
\section{Results} \label{Results}
\begin{itemize}  
\item Show the minimal model (to describe the sources and magnitude of error). This can go in supplement.
\begin{itemize}  
\item rendering error
\item isomerization error
\item ama error
\end{itemize}
\item Case 1. Only the target object color changes. AMA on isomerization
\item Case 2. Background color changes too, AMA on isomerization
\item Case 3. Background fixed, illuminant changes, AMA on isomerization fails, but the contrast version works
\item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better

@@

@@

%% Figure 9
\begin{figure}
\centering
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
        \caption{Luminance Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
    \caption{{\bf Receptive fields and luminance estimates. Case 1:} (a) First two receptive fields produced by the AMA. Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right). (b) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance. (c) The estimates of the target object standard luminance. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}

>>>>

% WHAT STORY DO WE WANT TO TELL ABOUT THE RESULTS
%  1) Case 0 -- work out effect of sources of internal noise - isomerization and AMA -- without any external "noise", where external "noise" is the effect of variability in object extrinsic scene factors (illumination, surrounding objects). 
%                      Also establish the rendering noise is einsy relative to whatever else we're doing.
%  2) Move to Case 1 -- what happens when we introduce color variability into the target.  This may not be of interest to the psychophysics, but none-the-less seems interesting to know as one ponders lightness constancy.
%  3) On to Case 2 -- here the question is, do we keep varying target color, or do we fix target color and vary illumination?  In any case, this isn't too hard a case if the other objects remain fixed, because then contrast coding basically normalizes out a lot of the variation, and it's only the spectral variation that might screw things up.  But, that's why we run case 3.
%  4) Do we run a case where the relative spectrum of the illuminant stays fixed and we only vary intensity?
%  4) On to Case 3 --
\section{Results} \label{Results}
\begin{itemize}  
\item Show the minimal model (to describe the sources and magnitude of error). This can go in supplement.
\begin{itemize}  
\item rendering error
\item isomerization error
\item ama error
\end{itemize}
\item Case 1. Only the target object color changes. AMA on isomerization
\item Case 2. Background color changes too, AMA on isomerization. (This is not giving good results. The filters are giving weights to the background which they should not. Maybe more samples would help.)
\item Case 3. Background fixed, illuminant changes, AMA on isomerization fails, but the contrast version works
\item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better

@@

%% Figure Results
\begin{figure}
\centering
    \begin{subfigure}[b]{0.33 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
        \caption{Rendering noise}
        \label{fig:renderingNoise}
    \end{subfigure}
        \begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
        \caption{Rendering and isomerization noise}
        \label{fig:renderingAndIsomerization}
    \end{subfigure}
        \begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
        \caption{Target color variation}
        \label{fig:renderingIsomerizationTargetColor}
    \end{subfigure}    
    \caption{Different sources of noise}
\label{fig:sourcesOfNoise}
\end{figure}

@@

%% Figure 9
\begin{figure}
\centering
    \begin{subfigure}[b]{0.4 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.27 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
        \begin{subfigure}[b]{0.27 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
        \caption{Luminance Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
    \caption{{\bf Receptive fields and luminance estimates. Case 1:} (a) First two receptive fields produced by the AMA. Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right). (b) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance. (c) The estimates of the target object standard luminance. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}

%% Figure Isomerization Fails
\begin{figure}
\centering
    \begin{subfigure}[b]{0.3	 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/isomerizationFails.pdf}
        \caption{AMA on isomerization fails in case of variation in illuminant}
        \label{fig:isomerizationFails}
    \end{subfigure}
    ~
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/constrastWorks.pdf}
        \caption{Converting signal to contrast solves the problem}
        \label{fig:constrastWorks}
    \end{subfigure}
    \caption{Need for contrast conversion.}
\label{fig:importanceOfConstrast}
\end{figure}
